### 2016-06-15 forgerard.tex
latest version of model and next thinkg to do.

The simplified implemented model is
\begin{equation}
\left(
\begin{matrix}
U_o-V_o\\B_o-V_o\\V_o-R_o\\V_o-I_o\\EW_{Si, o}\\ EW_{Ca, o}
\end{matrix}
\right) \sim \mathcal{N}
\left(
\left(
\begin{matrix}
c_0+\alpha_0 EW_{Si} + \beta_0 EW_{Ca} +\gamma_0 k  \\
c_1+\alpha_1 EW_{Si} + \beta_1 EW_{Ca}  +\gamma_1 k  \\
c_2+\alpha_2 EW_{Si} + \beta_2 EW_{Ca} +\gamma_2 k\\
c_3+\alpha_3 EW_{Si} + \beta_3 EW_{Ca} +\gamma_3 k\\
EW_{Si}\\ EW_{Ca}
\end{matrix}
\right)
,C
\right),
\end{equation}
The data are the colors and equivalent widths on the left side.  There are global parameters $c$, $\alpha$, $\beta$, and $\gamma$.  Each
supernova has parameters $EW_{Si}$, $EW_{Ca}$, and $k$.  To constrain the problem $\gamma_1=1$ and one supernova is selected to have
$k=0$.

The next level of complexity to add is intrinsic dispersion through stochastic parameters that describe the global  covariance matrices
$C_{c}$.  The model would then look like
\begin{equation}
\left(
\begin{matrix}
U-V\\B-V\\V-R\\V-I
\end{matrix}
\right) \sim \mathcal{N}
\left(
\left(
\begin{matrix}
c_0+\alpha_0 EW_{Si} + \beta_0 EW_{Ca} \\
c_1+\alpha_1 EW_{Si} + \beta_1 EW_{Ca}  \\
c_2+\alpha_2 EW_{Si} + \beta_2 EW_{Ca} \\
c_3+\alpha_3 EW_{Si} + \beta_3 EW_{Ca} 
\end{matrix}
\right)
,C_{c}
\right),
\end{equation}

\begin{equation}
\left(
\begin{matrix}
U_o-V_o\\B_o-V_o\\V_o-R_o\\V_o-I_o\\EW_{Si, o}\\ EW_{Ca, o}
\end{matrix}
\right) \sim \mathcal{N}
\left(
\left(
\begin{matrix}
U-V +\gamma_0 k \\B-V +\gamma_1 k \\V-R+\gamma_2 k\\V-I+\gamma_3 k\\
EW_{Si}\\ EW_{Ca}
\end{matrix}
\right)
,C
\right).
\end{equation}

>>>>

The simplified implemented model is
\begin{equation}
\left(
\begin{matrix}
U_o-V_o\\B_o-V_o\\V_o-R_o\\V_o-I_o\\EW_{Si, o}\\ EW_{Ca, o}
\end{matrix}
\right) \sim \mathcal{N}
\left(
\left(
\begin{matrix}
c_0+\alpha_0 EW_{Si} + \beta_0 EW_{Ca} +\gamma_0 k  \\
c_1+\alpha_1 EW_{Si} + \beta_1 EW_{Ca}  +\gamma_1 k  \\
c_2+\alpha_2 EW_{Si} + \beta_2 EW_{Ca} +\gamma_2 k\\
c_3+\alpha_3 EW_{Si} + \beta_3 EW_{Ca} +\gamma_3 k\\
EW_{Si}\\ EW_{Ca}
\end{matrix}
\right)
,C
\right),
\end{equation}
The data are the colors and equivalent widths on the left side, $C$ is the corresponding measurement
covariance.  There are global parameters $c$, $\alpha$, $\beta$, and $\gamma$.  Each
supernova has parameters $EW_{Si}$, $EW_{Ca}$, and $k$.  To constrain the problem $\gamma_1=1$ and one supernova is selected to have
$k=0$.

The next level of complexity to add is intrinsic dispersion through stochastic parameters that describe the global  covariance matrices
$C_{c}$.  The model would then look like
\begin{equation}
\left(
\begin{matrix}
U-V\\B-V\\V-R\\V-I\\V
\end{matrix}
\right) \sim \mathcal{N}
\left(
\left(
\begin{matrix}
c_0+\alpha_0 EW_{Si} + \beta_0 EW_{Ca} \\
c_1+\alpha_1 EW_{Si} + \beta_1 EW_{Ca}  \\
c_2+\alpha_2 EW_{Si} + \beta_2 EW_{Ca} \\
c_3+\alpha_3 EW_{Si} + \beta_3 EW_{Ca} \\
c_4+\alpha_4 EW_{Si} + \beta_4 EW_{Ca}
\end{matrix}
\right)
,C_{c}
\right),
\end{equation}

\begin{equation}
\left(
\begin{matrix}
U_o-V_o\\B_o-V_o\\V_o-R_o\\V_o-I_o\\V_o\\EW_{Si, o}\\ EW_{Ca, o}
\end{matrix}
\right) \sim \mathcal{N}
\left(
\left(
\begin{matrix}
U-V +\gamma_0 k \\B-V +\gamma_1 k \\V-R+\gamma_2 k\\V-I+\gamma_3 k\\V+\gamma_4 k\\
EW_{Si}\\ EW_{Ca}
\end{matrix}
\right)
,C
\right).
\end{equation}
